### 2019-10-01 socials.tex
adds alternative socials

>>>>

\subsubsection{Alternative Options}

Listed above are just a few of the many ideas for socials we've had. Here are some alternative social options that we can explore when we have more information.

\begin{itemize}
	\item Cocktail Hour at Krannert Center for the Performing Arts\\
	Krannert is UIUC's world famous performance center with a beautiful lobby area capable of holding up to 2000 people. They have a cocktail bar on site as well as a stage in the lobby.
\end{itemize}
